---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nucommit

<!-- badges: start -->
<!-- badges: end -->

The goal of nucommit is to calculate the *N*umbers, *U*nity and *Commit*ment metrics from tweet data (usually collected by rtweet::search_tweet or scrapers such as [twitterscraper](https://github.com/taspinar/twitterscraper)) using the method by Freelon, McIlwain & Clark (2019).

References:
1. Freelon, D., McIlwain, C., & Clark, M. (2018). Quantifying the power and consequences of social media protest. New Media & Society, 20(3), 990-1011.

## Installation

``` r
devtools::install_github("chainsawriot/nucommit")
```

## Example

Some tweets collected by search_tweets("#rstats")

```{r example1}
library(nucommit)
library(tibble)
data(rt)
rt
```

Calculate the Numbers time series data

```{r numbers}
calculate_numbers(rt)
```

Calculate the Unity time series data

```{r unity}
calculate_unity(rt)
```

Calculate the Commitment time series data

```{r commitment}
calculate_commitment(rt)
```
